---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# piercer

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

The goal of [*piercer*](https://github.com/sjpierce/piercer) is to provide a set 
of functions and files written for use in my personal research and statistical
collaboration and consulting work. Packaging them is a learning experience, a 
way to shorten my other scripts, and a way to increase quality, reproducibility,
and efficiency.

## Installation
This package is not yet available from [CRAN](https://CRAN.R-project.org). 
Releasing it there is a long-term goal. Meanwhile, the development version of
*piercer* can be installed from the source stored in a public
[GitHub](https://github.com) repository using the 
[*devtools*](https://devtools.r-lib.org/) package. Precompiled binary 
installer files are not available at this time, so installing from the source
code is the only option. 

### Order of Installation Tasks
Before installing *piercer*, make sure you have:

* Installed R 4.1.0 or later. You can get the most recent version of R from the 
  [Comprehensive R Archive Network (CRAN)](https://cran.r-project.org/). 
* Installed any tools required for compiling packages (they will be specific
  to your operating system). These will be necessary for the *devtools* package
  to work. 
    * On Windows, see https://cran.r-project.org/bin/windows/Rtools/. 
    * On Mac OS X, see https://cran.r-project.org/bin/macosx/tools and 
      https://mac.R-project.org/tools/. 
* Installed the *devtools* package. The most recent 
  [CRAN release of *devtools*](https://cran.r-project.org/package=devtools) 
  will likely be more stable but sometimes you may instead need the 
  [development version at GitHub](https://github.com/r-lib/devtools).
* Updated your R packages. You may be prompted with a dialog box asking "Do you 
  want to install from sources the packages which need compilation?" It usually 
  works fine if I choose "no". Occasionally, it appears necessary to choose 
  "yes", but I am more likely to run into problems when doing that.  
* After those tasks are done, you can install *piercer*.

If you only need *piercer* because a script you want to run loads the package 
and uses one of its functions, then type the following code in the R 
console to install the package to your package library. You will need internet
access for this to work.

```{r install-piercer-Windows, echo = TRUE, eval = FALSE}
devtools::install_github("sjpierce/piercer")
```

That should enable you to use the functions built into the package. Depending on
how your computer and R installation are configured, that may either install 
R to the main R package library, or to a personal package library. If you do not
have write permissions to the main R package library, then R will ask if you 
want to use a personal package library instead. 

## Example
One thing I have been contemplating recently is how to implement some of the 
American Statistical Association's recent recommendations on moving away from 
interpreting p-values in terms of statistical significance (Wasserstein, Schirm,
& Lazar, 2019). I found the suggestions to convert p-values into s-values
(Greenland, 2019), Bayes Factor Bounds (BFBs; Benjamin & Berger, 2019), and 
posterior probabilities that H1 is true (Benjamin & Berger, 2019) interesting, 
so I wrote some functions to do those conversions. 

The example below shows how to apply my *convertp* function. I use one of the 
examples for the base R *ttest* function to demonstrate it. 

```{r example}
library(piercer)
tresult <- t.test(1:10, y = c(7:20))
tresult

# Convert p-value into s-value, BFB, & posterior probability that H1 is true. 
convertp(p = tresult$p.value, digits = 3)
```

## References
Benjamin, D. J., & Berger, J. O. (2019). Three recommendations for improving the
use of p-values. *The American Statistician, 73*(Supplement 1), 186-191. 
[doi:10.1080/00031305.2018.1543135](https://doi.org/10.1080/00031305.2018.1543135)

Bryan, J., & Hester, J. (n.d.). *What they forgot to teach you about R*. 
https://rstats.wtf

Greenland, S. (2019). Valid p-values behave exactly as they should: Some 
misleading criticisms of p-values and their resolution with s-values. 
*The American Statistician, 73*(Supplement 1), 106-114.
[doi:10.1080/00031305.2018.1529625](https://doi.org/10.1080/00031305.2018.1529625)

Wasserstein, R. L., Schirm, A. L., & Lazar, N. A. (2019). Moving to a world
beyond "p < .05". *The American Statistician, 73*(Supplement 1), 1-19. 
[doi:10.1080/00031305.2019.1583913](https://doi.org/10.1080/00031305.2019.1583913)

## Task List 
* Add assertthat checks to more functions.
* Add more testthat unit tests for functions.
