---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# piercer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/piercer)](https://CRAN.R-project.org/package=piercer)
<!-- badges: end -->

The goal of [piercer](https://github.com/sjpierce/piercer) is to provide a set 
of functions and files written for use in my personal research and statistical
consulting work. Packaging them is a learning experience, a way to shorten my
other scripts, and a way to increase quality, reproducibility, and efficiency.

## Task List 
* Add assertthat checks to:
    * *DI()* arguments in `R/Categorical_Data_Functions.R`
    * *rxx.NL()* arguments in `R/NL-SEM_Reliability.R`
    * *p2odds()* arguments in `r/Transform_Functions.R`
    * *p2or()* arguments in `r/Transform_Functions.R`
    * *tag_um()* arguments in `r/Data_Management_Functions.R`
* Add more testthat unit tests for various functions:
    * *ci.rpc()* 
    * *ci.rp()*
    * *r.ps()*
    * *r.pc()*
    * *r.p*
    * *DI()*
    * *Fisher_r2z()*
    * *Fisher_z2r()*
    * *rxx.NL()*
    * *tag_um()*

## Installation
This package is not yet available from [CRAN](https://CRAN.R-project.org). 
Releasing it there is a long-term goal. Meanwhile, the development version of
*piercer* can be installed from [GitHub](https://github.com) using the 
[*devtools*](https://devtools.r-lib.org/) package. 

### Order of Installation Tasks
Before installing piercer, make sure you have:

* Installed R 4.0.0 or later.
* Installed any tools required for compiling packages (they will be specific
  to your operating system). These will be necessary for the *devtools* package
  to work. 
    * On Windows, see https://cran.r-project.org/bin/windows/Rtools/. 
    * On Mac OS X, see https://cran.r-project.org/bin/macosx/tools and 
      https://mac.R-project.org/tools/.
* Installed the *devtools* package. The most recent 
  [CRAN release of *devtools*](https://cran.r-project.org/package=devtools) 
  will likely be more stable but sometimes you may instead need the 
  [development version at GitHub](https://github.com/r-lib/devtools).
* Updated your R packages. You may be prompted with a dialog box asking "Do you 
  want to install from sources the packages which need compilation?" Most of the
  things work fine if I choose "no". Occasionally, it appears necessary to 
  choose "yes", but I am more likely to run into problems when doing that.  

After those tasks are done, you can install *piercer* using the following code.

```r
devtools::install_github("sjpierce/piercer")
```

```{r, echo = FALSE, eval = FALSE}
devtools::install_github("sjpierce/piercer")
```

### Normal Install (MS Windows, version 10)
My normal scenario involves installing the package into an R package library 
located on a computer's own hard drive (e.g., 
**C:/Users/Username/Documents/R/win-library/4.0** or 
**C:/Program Files/R/R-4.0.0/library**). At one point I experimented with     
installing the package to a personal R package library stored on a Windows 
network share (i.e., in a user's profile that is located by a share name
such as 
**\\\\\\\\server/Redirected_Folders/username/Documents/R/win-library/4.0**). 
That was a bit more cumbersome than I preferred and the performance was slow, so  
I have omitted instructions for that scenario. 

### Normal Install (Apple Mac OS X, Catalina, version 10.15)
Notes here are based on testing conducted on 2020-03-06 with a colleague who
uses Mac OS, then updated after the release of R 4.0.0. Instead of Rtools (used
on MS Windows), you need to install Mac OS specific development tools for
compiling R packages. The code shown above should work to install this package
after the right tools are in place. 

## Example
One thing I have been contemplating recently is how to implement some of the 
American Statitical Association's recent recommendations on moving away from 
interpreting p-values in terms of statistical significance (Wasserstein, Schirm,
& Lazar, 2019). I found the suggestions to convert p-values into s-values
(Greenland, 2019), Bayes Factor Bounds (BFBs; Benjamin & Berger, 2019), and 
posterior probabilities that H1 is true (Benjamin & Berger, 2019) interesting, 
so I wrote some functions to do those conversions. 

The example below shows how to apply my *convertp* function. I use one of the 
examples for the base R *ttest* function to demonstrate it. 

```{r example}
library(piercer)
tresult <- t.test(1:10, y = c(7:20))
tresult

# Convert p-value into s-value, BFB, & posterior probability that H1 is true. 
convertp(p = tresult$p.value, digits = 3)
```

## References
Benjamin, D. J., & Berger, J. O. (2019). Three recommendations for improving the
use of p-values. *The American Statistician, 73*(Supplement 1), 186-191. 
[doi:10.1080/00031305.2018.1543135](https://doi.org/10.1080/00031305.2018.1543135)

Greenland, S. (2019). Valid p-values behave exactly as they should: Some 
misleading criticisms of p-values and their resolution with s-values. 
*The American Statistician, 73*(Supplement 1), 106-114.
[doi:10.1080/00031305.2018.1529625](https://doi.org/10.1080/00031305.2018.1529625)

Wasserstein, R. L., Schirm, A. L., & Lazar, N. A. (2019). Moving to a world
beyond "p < .05". *The American Statistician, 73*(Supplement 1), 1-19. 
[doi:10.1080/00031305.2019.1583913](https://doi.org/10.1080/00031305.2019.1583913)
