---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# piercer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/piercer)](https://CRAN.R-project.org/package=piercer)
<!-- badges: end -->

The goal of [piercer](https://github.com/sjpierce/piercer) is to provide a set 
of functions and files written for use in my personal research and statistical
consulting work. Packaging them is a learning experience, a way to shorten my
other scripts, and a way to increase quality, reproducibility, and efficiency.

## Task List 
* Add assertthat checks on *rxx.NL()* arguments in `R/NL-SEM_Reliability.R`. 
* Add testthat unit tests for *rxx.NL()*.
* Add more testthat unit tests for various functions. 
* Add a function to compute confidence intervals for Pearson correlations.

## Installation
This package is not yet available from [CRAN](https://CRAN.R-project.org). 
Releasing it there is a long-term goal. Meanwhile, the development version can 
be installed from [GitHub](https://github.com) using the *devtools* package.

### Normal Install
A normal install scenario involves installing the package into an R package 
library located on a computer's own hard drive (e.g., 
**C:/Users/Username/Documents/R/win-library/3.6** or 
**C:/Program Files/R/R-3.6.1/library**) instead of on a Windows network share. 

In a normal install scenario, use the following code. If you don't have
*devtools* installed, uncomment that line first. It is possible that you also
need to install the latest recommended version of 
[Rtools](https://cran.r-project.org/bin/windows/Rtools) first. 

```r
# install.packages("devtools")
devtools::install_github("sjpierce/piercer")
```

```{r, echo = FALSE, eval = FALSE}
# install.packages("devtools")
devtools::install_github("sjpierce/piercer")
```

### Install on a Windows Network Share
Instructions to be written later. The process is more involved when you intend
to install the package to a personal R package library that is stored on a 
Windows network share (i.e., in a user's profile that is located by a share name
such as 
**\\\\\\\\server/Redirected_Folders/username/Documents/R/win-library/3.6**). 

## Example
One thing I have been contemplating recently is how to implement some of the 
American Statitical Association's recent recommendations on moving away from 
interpreting p-values in terms of statistical significance (Wasserstein, Schirm,
& Lazar, 2019). I found the suggestions to convert p-values into s-values
(Greenland, 2019), Bayes Factor Bounds (BFBs; Benjamin & Berger, 2019), and 
posterior probabilities that H1 is true (Benjamin & Berger, 2019) interesting, 
so I wrote some functions to do those conversions. 

The example below shows how to apply my *convertp* function. I use one of the 
examples for the base R *ttest* function to demonstrate it. 

```{r example}
library(piercer)
tresult <- t.test(1:10, y = c(7:20))
tresult

# Convert p-value into s-value, BFB, & posterior probability that H1 is true. 
convertp(p = tresult$p.value, digits = 3)
```

## References
Benjamin, D. J., & Berger, J. O. (2019). Three recommendations for improving the
use of p-values. *The American Statistician, 73*(Supplement 1), 186-191. 
[doi:10.1080/00031305.2018.1543135](https://doi.org/10.1080/00031305.2018.1543135)

Greenland, S. (2019). Valid p-values behave exactly as they should: Some 
misleading criticisms of p-values and their resolution with s-values. 
*The American Statistician, 73*(Supplement 1), 106-114.
[doi:10.1080/00031305.2018.1529625](https://doi.org/10.1080/00031305.2018.1529625)

Wasserstein, R. L., Schirm, A. L., & Lazar, N. A. (2019). Moving to a world
beyond "p < .05". *The American Statistician, 73*(Supplement 1), 1-19. 
[doi:10.1080/00031305.2019.1583913](https://doi.org/10.1080/00031305.2019.1583913)
